\bf\mftitle

### 2011-02-28 doc/jInfer/projecttype/projecttype.tex
#3187361 projecttype doc

\jmodule{ProjectType} is the module representing a jInfer project in the NB platform, which groups input/output files that belongs to one specific inference. Each jInfer project also allows user to set properties specific for inference.\\

@@

\section{Structure}
PropertiesPanelProvider
Structure of \jmodule{ProjectType} can be divided into following five main parts.
\begin{itemize}
	\item Base classes - Classes providing main functionality like creation of project, defining operations like move, delete, copy etc. All the base classes are contained in the \code{cz.cuni.mff.ksi.jinfer.projecttype} package.
	\item Visualization classes - These classes create tree structure of project in NBP Projects view and are contained in the \code{cz.cuni.mff.ksi.jinfer.projecttype.nodes}.
	\item Actions - Classes from \code{cz.cuni.mff.ksi.jinfer.projecttype.actions} package that provides actions allowing adding, removing input files into project, or running the project.
	\item Properties - Classes responsible for creation of project properties window with properties category tree. These are situated in  \code{cz.cuni.mff.ksi.jinfer.projecttype.properties} package.
	\item Project wizard - Classes representing creation of project through new project wizard from  \code{cz.cuni.mff.ksi.jinfer.projecttype.sample} package.
\end{itemize}

@@

Run action, which is available in root node context menu, is also present in NBP toolbar as a \emph{Run} button and in jInfer Welcome window. This action is implemented in \code{RunAction} class and simply invokes \jmodule{Runner}s \code{run()} method, if no other inference is already running, otherwise information dialog pops up informing about already running inference. This check is done with \code{setActiveProject()} from \code{RunningProject} class.

@@

>>>>

\jmodule{ProjectType} is the module representing a jInfer project in the NB platform, which groups input/output files that belongs to one specific inference. Each jInfer project also allows user to set properties specific for a inference.\\

@@

\section{Structure}

Structure of \jmodule{ProjectType} can be divided into following five main parts.
\begin{itemize}
	\item Base classes - Classes providing main functionality like creation of project, defining operations like move, delete, copy etc. All the base classes are contained in the \code{cz.cuni.mff.ksi.jinfer.projecttype} package.
	\item Visualization classes - These classes create tree structure of project in NBP Projects view and are contained in the \code{cz.cuni.mff.ksi.jinfer.projecttype.nodes}.
	\item Actions - Classes from \code{cz.cuni.mff.ksi.jinfer.projecttype.actions} package that provides actions allowing adding input files into project, removing input files, or running the project.
	\item Properties - Classes responsible for creation of project properties window with properties category tree. These are situated in  \code{cz.cuni.mff.ksi.jinfer.projecttype.properties} package.
	\item Project wizard - Classes representing creation of project through new project wizard from  \code{cz.cuni.mff.ksi.jinfer.projecttype.sample} package.
\end{itemize}

@@

Run action, which is available in root node context menu, is also present in NBP toolbar as a \emph{Run} button and in jInfer Welcome window. This action is implemented in \code{RunAction} class and simply invokes \jmodule{Runner}s \code{run()} method, if no other inference is already running, otherwise information dialog pops up informing about already running inference. This check is done with \code{setActiveProject()} from \code{RunningProject} class (section \ref{running-project}).

@@

\subsection{RunningProject utility class}\label{running-project}

This section describes \code{RunningProject} utility class, which is not part of the \jmodule{ProjectType} module, but is closely related to it. This class can be found in a \code{cz.cuni.mff.ksi.jinfer.base.utils} package in the \jmodule{Base} module. The main purpose of this class is to allow all jInfer \jmodule{module}s to access \code{JInferProject} instance of the actual running inference. Notice that in jInfer application can be only one running inference at a time.\\

\noindent \code{RunningProject} class implements these methods:
\begin{itemize}
	\item \code{setActiveProject()} - Setter of the \code{JInferProject} instance of a running project, which set the \code{JInferProject} instance if no other inference is running (no other \code{JInferProject} instance is already set). Returns \code{boolean} value, according as the setting was successful or not.
	\item \code{removeActiveProject()} - Removes \code{JInferProject} instance if some inference is running.
	\item \code{getActiveProject()} - Getter of the \code{JInferProject} instance of a running project.
	\item \code{isActiveProject()} - Checks if some inference is running (the \code{JInferProject} instance is set).
	\item \code{getActiveProjectProps()} - Gets \code{Properties} instance of the actual running inference (\code{Properties} instance is part of the \code{JInferProject} instace).
	\item \code{getNextModuleCaps()} - Getter of a capability of the next module in the inference chain.
	\item \code{setNextModuleCaps()} - Setter of a capability of the next module in the inference chain.
\end{itemize}
